---
title: "RWorksheet_#3b"
author: "Kathrina Casandra Sison"
date: "2024-10-14"
output: html_document
---
1. Create a data frame using the table below.

a. Write the codes.
```{r}
respo_data <- data.frame(
Respondents = 1:20,
Sex = c(2, 2, 1, 2, 1, 2, 1, 2, 1, 2, 1, 1, 2, 2, 1, 1, 2, 1, 2, 1),
Fathers_Occupation = c(1, 3, 1, 3, 3, 1, 3, 2, 3, 1, 2, 1, 3, 1, 3, 1, 3, 1, 3, 1),
Persons_at_Home = c(5, 7, 3, 8, 9, 6, 9, 6, 4, 3, 4, 5, 7, 8, 3, 7, 11, 7, 6, 6),
Siblings_at_School = c(6, 4, 4, 1, 1, 3, 3, 5, 3, 2, 4, 2, 3, 4, 3, 3, 5, 3, 2, 2),
Types_of_Houses = c(1, 2, 1, 1, 3, 3, 3, 2, 1, 3, 1, 2, 1, 3, 1, 3, 1, 3, 2, 2)
)
```

b. Describe the data. Get the structure or the summary of the data

```{r}
str(respo_data)
```

c. Is the mean number of siblings attending is 5?
```{r}
mean_siblings <- mean(respo_data$Siblings_at_School)
mean_siblings == 5
mean_siblings
```
d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.

```{r}
subset_data <- respo_data[1:2, ]
subset_data
```

e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r}
subset_data_2 <- respo_data[c(3, 5), c(2, 4)]
subset_data_2
```

f. Select the variable types of houses then store the vector that results as types_houses. Write the codes.

```{r}
types_houses <- respo_data$Types_of_Houses
types_houses
```
g. Select only all Males respondent that their father occupation was farmer. Write the codes and its output.
```{r}
male_farmers <- subset(respo_data, Sex == 1 & Fathers_Occupation == 1)
male_farmers
```
h. Select only all females respondent that have greater than or equal to 5 number of siblings attending school. Write the codes and its outputs.

```{r}
female_siblings <- subset(respo_data, Sex == 2 & Siblings_at_School >= 5)
female_siblings
```

2. Write a R program to create an empty data frame. Using the following codes:
df = data.frame(Ints=integer(),

```{r}
df = data.frame(Ints=integer(),
Doubles=double(), CharacterS=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
```
3. 
a.
```{r}
setwd("C:/Users/Admin/Documents")
householdData_data <- read.csv("HouseholdData.csv", header = TRUE, sep = ",")
head(householdData_data)
```

B.Convert the Sex into factor using factor() function and change it into integer.[Legend:Male = 1 and Female = 2]. Write the R codes and its output.

```{r}
household_data <- data.frame(
Respondents = 1:10,
Sex = c("Male", "Female", "Female", "Male", "Male",
"Female", "Female", "Male", "Female", "Male"),
Fathers_Occupation = c("Farmer", "Farmer", "Farmer", "Farmer", "Driver",
"Driver", "Driver", "Driver", "Others", "Others"),
Persons_at_Home = c(5, 7, 3, 8, 1, 2, 4, 3, 1, 6),
Siblings_at_School = c(5, 7, 3, 8, 1, 4, 2, 6, 11, 6),
Types_of_Houses = c("Wood", "Concrete", "Concrete", "Wood", "Semi-concrete",
"Semi-concrete", "Concrete", "Wood", "Semi-concrete", "Concrete"))
household_data

household_data$Sex <- factor(household_data$Sex, levels = c("Male", "Female"), labels = c(1, 2))
household_data$Sex

```

c. Convert the Type of Houses into factor and change it into integer. [Legend: Wood
= 1; Congrete = 2; Semi-Congrete = 3]. Write the R codes and its output.

```{r}
household_data$Types_of_Houses <- factor(household_data$Types_of_Houses,
levels = c("Wood", "Concrete", "Semi-concrete"), labels = c(1, 2, 3))
household_data$Types_of_Houses
```
d. On father’s occupation, factor it as Farmer = 1; Driver = 2; and Others = 3. What
is the R code and its output?


```{r}
household_data$Fathers_Occupation <- factor(household_data$Fathers_Occupation,
levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))
household_data$Fathers_Occupation
```
e. Select only all females respondent that has a father whose occupation is driver. Write
the codes and its output.
```{r}
female_driver <- subset(household_data, Sex == 2 & Fathers_Occupation == "Driver")
female_driver
```

f. Select the respondents that have greater than or equal to 5 number of siblings attending school. Write the codes and its output.
```{r}
siblings_5_or_more <- subset(household_data, Siblings_at_School >= 5)
print(siblings_5_or_more)
```

4. Interpret the graph.
The graph shows the different sentiment based on its color. The highest sentiment of tweets was negative and the lowest is neutral.