---
title: "RWorksheet_Sison#4."
author: "Kathrina Casandra Sison"
date: "2024-10-14"
output: html_document
---


```{r}
Shoe_Size <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
Height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.75, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
Gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
shoe_data1 <- data.frame(Shoe_Size,Height, Gender)
```

1. The table below shows the data about shoe size and height. Create a data frame.

#a. Describe the data.
The data is consist of different shoe sizes along with its height and gender of the user.

#b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.

```{r}
str(shoe_data1)
male_subset <- shoe_data1[shoe_data1$Gender == "M",]
female <- shoe_data1[shoe_data1$Gender == "F",]
print("Male_subset")
print(male_subset)
print("Female Susbet")
female
```

c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.

```{r}
Shoe_Size <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
Height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.75, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
mean_shoe_size <- mean(Shoe_Size)
mean_height <- mean(Height)
mean_shoe_size
mean_height
```


d. Is there a relationship between shoe size and height? Why?

```{r}
correlation <- cor(shoe_data1$Shoe_Size, shoe_data1$Height, use = "complete.obs")
print(paste("Correlation between Shoe Size and Height:", correlation))
```

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
Consider data consisting of the names of months:
"March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August", "July","December","August","August","September","November","February",
April")

```{r}
months <- c("March", "April", "January", "November", "January",
            "September", "October", "September", "November", "August",
            "January", "November", "November", "February", "May", "August",
            "July", "December", "August", "August", "September", "November", 
            "February", "April")
factor_months_vector <- factor(months)

print(factor_months_vector)
print(levels(factor_months_vector))
```
3. Then check the summary() of the months_vector and factor_months_vector. | Inter-pret the results of both vectors. Are they both equally useful in this case?

```{r}
factor_months <- factor(months)
summary(months)
summary(factor_months)
```
4. Create a vector and factor for the table below.

```{r}
direction <- c("East", "West", "North")
frequency <- c(1, 4, 3)
factor_data <- factor(direction, levels = c("East", "West", "North"))
print(factor_data)

new_order_data <- factor(factor_data, levels = c("East", "West", "North"))
print(new_order_data)
```

5. 

```{r}
write.csv("import_march.csv", row.names = FALSE)
data <- read.table("import_march.csv", header = TRUE, sep = ",")
```
